A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Remove useless introduction and rewrite the advantage of transparency

\subsection{Enable Automated Trading Process}
Ethereum smart contract can make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures. Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream. The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. Preserving a consumer list on Product Contract functions like the reputation of the product, the better the quality the more the consumers he/her has, which are key references for data consumers to decide whether to subscribe.

>>>>

\subsection{Enable Automated Trading Process}
With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures. Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream. The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.

Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress. Moreover, binding the encryption key with the transparent subscription procedure on Product Contract allows data providers to track and manage the authorized user list, and allows data consumers to always have access after payment, even if the key is lost.
